%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page 
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%		
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin]{res}  

% Default font is the helvetica postscript font
\usepackage{helvet}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{Joshua Schmidt}

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

\address{\\LinkedIn : https://linkedin.com/in/joshua-n-schmidt
\\Github : https://github.com/jschmidtnj
}
\address{joshuanschmidt@gmail.com \\(908) 531-7087\\Website : https://joshuaschmidt.tech\\}

% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------

\begin{resume}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{OBJECTIVE}
{\sl Computer Engineering Student at Stevens. Hardworking, creative and determined. 
  Looking for internship opportunities where I can apply my skills and contribute to interesting projects}

\section{EDUCATION}
\textbf{Stevens Institute of Technology}, Hoboken, NJ \hfill GPA: 3.99/4\\
{\sl Bachelors of Engineering}, Computer Engineering\\
Expected May, 2022 \\
\textbf{Watchung Hills Regional High School}, Warren, NJ\\
{\sl Graduated June 2017}

%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{TECHNICAL\\SKILLS}

\textbf{Languages: } Python, C++, Java, Javascript, Golang, Dart (Flutter)
\\
\textbf{Databases: } MySQL / Postgres, MongoDB, SQLite, Redis, Elasticsearch
\\
\textbf{Cloud: } AWS, GCP, Azure
\\
\textbf{Tools/Frameworks: } Git, Linux, ROS, Node.js, Vue.js, React.js, Graphql, REST,
PyTorch, Nuxt, Firebase, Wordpress, BeautifulSoup, PlatformIO, WebRTC
\\
\textbf{Familiar: } Matlab, HTML, CSS, Tensorflow, Jupyter Notebooks
\\
\textbf{General: } Data Structures, Algorithms, OOP

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{EXPERIENCE}

\textbf{Bell Labs - Robotics Development Internship \hfill{May '18 - Aug '18}\\}
\normalfont{\textbullet{}{\sl Swerve Drive Robot: } The summer was spent updating a swerve drive robot to work on ROS. This required many changes on both the 
  hardware and software side, as the robot needed new motorcontrollers, motors, microprocessor, etc., as well as compatible kinematics software for the swerve drive. 
  Then this software needed to be integrated into the ROS stack, with accurate feedback from the motorcontrollers for distance and speed, as well as lidar and imu data.
  Modularity added to top and front of robot for easy modification and experimentation.\\}
\normalfont{\textbullet{}{\sl Bell Labs Innovation Award}}

\textbf{L3 Technologies - Software Engineering Internship \hfill{Jan '18 - May '18}\\}
\normalfont{\textbullet{}{\sl ANTX demo: } Created new drivers for RT2200a and Vortex radios. Interfaced  with PRC117 and Cisco wifi router to send network traffic 
  and monitor data throughput. Used this data to dynamically adjust network data, including a p2p video stream (WebRTC) and text chat (udp). Simulated network jamming 
  and throttling, dynamically changing frequency and band. Used Node.js, Vue.js, Java, Springboot, etc.\\}
\normalfont{\textbullet{}{\sl AACN development: } Agile product development for managing radio systems. Created interfaces to legacy codebase, created Docker containers 
  for production environment, created websocket notification system, and implemented put commands endpoint in device manager.}

\textbf{Colgate Palmolive - Google IT Internship \hfill{May '18 - Aug '18}\\}
\normalfont{\textbullet{}{\sl Workflow Responsive Web App: } Designed and created a website for employees to implement their own workflows
 - forms with approval chains - such as travel expenses, work-orders, and surveys. Deployed using Firebase database, hosting, serverless functions,
 storage, using jQuery and Vue.js for UI.\\}
\normalfont{\textbullet{}{\sl Active Drive Audit: } Created real-time software for logging Google Drive data, flagging users that have downloaded or
 externally shared too many files. Email alerts a Google group, linked to system admins. Used Google admin and reports apis, mailjet, app engine, Kubernetes,
 Golang, Jenkins CI/CD.\\}
\normalfont{\textbullet{}{\sl Daily Directory Update: } Developed software to update Google Directory with latest information from HR, including employee 
  name, email, status, address, and work location. Input from csv files, parsed and sorted for api output.\\}

%-------------------------------------------------------------------------------

\section{PROJECTS}

\employer{YHacks}
\location{Yale University, CT}
\title{\textbf{ \hfill Oct 2018}
 }
% \begin{itemize}
\normalfont{\textbullet{} Developed an application that scrapes facebook posts and ranks them on their perceived authenticity and accuracy. This was used
  to characterize news posts and look for fake news.}
% \end{itemize}
\begin{itemize}
\item {\sl Tech: } Scikit Learn, BeautifulSoup
\end{itemize}
\begin{itemize}
\item {\sl Link: } https://github.com/abouelkhair5/fakebook
\end{itemize}

\employer{BostonHacks}
\location{Bostom University, MA}
\title{\textbf{ \hfill May 2017}
 }
% \begin{itemize}
\normalfont{\textbullet{} Developed an Augmented Reality mobile application and framework, addressing the future of education, 
  utilizing machine learning and open-source tools to create a working prototype.}
% \end{itemize}
\begin{itemize}
\item {\sl Tech: } ARKit, iOS
\end{itemize}
\begin{itemize}
\item {\sl Link: } https://github.com/byliuyang/Linguis
\end{itemize}

%-------------------------------------------------------------------------------

\section{RELEVANT\\COURSES}
\par
\normalfont{\textbullet{} Intro to Comp Sci}
\normalfont{\textbullet{} Data Structures}
\normalfont{\textbullet{} Algorithms}
\normalfont{\textbullet{} Information Systems Engineering}
\normalfont{\textbullet{} Microprocessor Systems}
\normalfont{\textbullet{} Image Processing}

\section{ADDITIONAL ACTIVITIES}

\normalfont{\textbullet{} Treasurer of Stevens Ultimate}
\normalfont{\textbullet{} Founder of Business Collaboration Tool Startup}
\normalfont{\textbullet{} NASA SUITS}

%-------------------------------------------------------------------------------

\end{resume}
\end{document}
