%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Assemblers Software Internship} % Job title
  {NASA Langley Research Center} % Organization
  {Langley, Virginia} % Location
  {May 2021 - Aug. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Created a Software in the Loop Simulation of the Assemblers robot system, incorporating a physics engine and a real-time messaging service (DDS). Developed realistic simulations of all hardware components, including joint controllers, the IMU, and cameras, which are fully interoperable with the real hardware.}
      \item {Designed and implemented a user interface for visualizing and recording the simulation. Used 3D models of the modular Stewart platforms to accurately display the robot interacting with elements on the lunar surface. This desktop application was built with Qt, Python, and C++. Integrated with the trajectory generator and executor to show log messages in the UI.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Civic Digital Fellowship, Software Engineer} % Job title
  {U.S. Census Bureau} % Organization
  {Washington, D.C.} % Location
  {May. 2020 - Aug. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Edit Rules Parsing: Created NLP system for extracting and parsing pseudocode from 500+ page text documents, converting to an abstract object-oriented hierarchy. Datastructure used to produce executable Python code, for validating decennial data.}
      \item {Spark Proxy \& Dashboard: Created a proxy script to route requests to the Spark UI and Spark History UI through a path in the dashboard web server, enabling access to the UI without ssh port forwarding. Required html parsing for rewriting url paths. Additionally created reporting features for Differential Privacy System in the dashboard. Used Python, C++, Spark, REST}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Robotics Development Internship} % Job title
  {Nokia Bell Labs} % Organization
  {Murray Hill, NJ} % Location
  {May 2019 - Aug. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Swerve Drive Robot: Updated fully autonomous swerve drive robot platform to work on ROS. Required substantial changes in hardware and software, as robot needed new motorcontrollers, motors, microprocessor, and kinematics software for the drivetrain.}
      \item {Integrated drivetrain control software into ROS stack, with accurate odometry (feedback) from encoder, lidar, computer vision and imu data. Modularity added for easy modification and experimentation, with ability to hot-swap sensors and end effectors. Used Python, C++, ROS}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Engineering Internship} % Job title
  {L3 Harris} % Organization
  {Philadelphia, PA} % Location
  {Jan. 2019 - May 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {ANTX demo: Created new drivers for RT2200a and Vortex radios. Interfaced  with PRC117 and Cisco wifi router to send network traffic and monitor data throughput. Used this data to dynamically adjust network data, including a p2p video stream (WebRTC) and text chat (udp). Simulated network jamming and throttling, dynamically changing frequency and band. Used Java, Vue.js, Node.js, Springboot}
      \item {AACN development: Agile product development for managing radio systems. Created interfaces to legacy codebase, created Docker containers for production environment, added websocket notification system, and implemented put commands endpoint in device manager. Used Docker, Java, UDP + TCP sockets, Gradle, Springboot}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Google IT Internship} % Job title
  {Colgate Palmolive} % Organization
  {Piscataway, NJ} % Location
  {May 2018 - Aug. 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Workflow Responsive Web App: Designed and created webapp for employees to implement their custom workflows -- forms with approval chains -- such as travel expenses, work-orders, surveys. Deployed using Firebase database, hosting, serverless functions,
      storage, using jQuery and Vue.js for UI.}
      \item {Daily Directory Update: Developed software to update Google Directory with latest information from HR, (employee name, email, etc).}
      \item {Active Drive Audit: Created logging program for Google Drive data, flagging suspect users, with email alerts. Used Google admin and reports apis, mailjet, app engine, Kubernetes, Go, Jenkins}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
