%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Rental Application Automation Tool} % Organization
  {\href{https://flexapp.ai}{FlexApp AI}} % Project title
  {New York, NY} % Location
  {Dec. 2021 - June 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of what you did
      \item {Cofounder of FlexApp, a tool that makes it easy for prospective renters to apply for apartments, and property managers to review applications.}
      \item {Lead developer of five-person team, created novel AI tools that read PDFs and converted the text to and from consistent formats, solving a major pain-point for both applicants and realtors.}
      \item {Created a React \& Next.js based web app deployed to AWS for managing applications and making the submittion process as seamless as possible, with one-click applications.}
      \item {Built AI models for matching applicants with the best rentals for their credit history and financial constraints. Created tools for interfacing with Plaid and banking data, to support renters who are under-banked.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Stevens Student Managed Investment Fund} % Organization
  {\href{https://bailey.ssmif.com}{SSMIF}} % Project title
  {Hoboken, NJ} % Location
  {Aug. 2020 - May 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of what you did
      \item {Lead developer of a team of 15 quantitative analysts and software engineers managing an endowment fund worth over \$700k.}
      \item {Created a factor model for analyzing past and projected performance of the fund. Leverages several ML models --- Arima Regression, Random Forest, Attention-based Neural Networks --- built with Tensorflow and Scikit learn using C++ and Python.}
      \item {Built a React \& Next.js based web app deployed to AWS for executing transactions, visualizing performance, and running the factor model.}
      \item {Developed Lambda functions to automate fetching \& analyzing ticker data, generating excel reports, and running GitHub Actions CI / CD updates.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {a better way to search for code} % Organization
  {\href{https://rescribe.dev}{reScribe}} % Project title
  {Hoboken, NJ} % Location
  {Oct. 2020 - July 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of what you did
      \item {Software development lead, working with 5 designers and engineers to build the most advanced source code search and analysis tool.}
      \item {Created a scalable, NLP-based algorithm for indexing open-source code. Used ANTLR4 to parse code syntax, and integrated with Elasticsearch.}
      \item {Designed a public authenticated GraphQL API for integrating with client-facing applications, including a first-party web app (created using Gatsby), VSCode extension, and GitHub App (for CI/CD integration). Over 10k repositories indexed.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  % \cventry
  % {Encouraging Women Across All Borders} % Organization
  % {\href{https://ewaab.org}{EWAAB Network}} % Project title
  % {NYC, NY} % Location
  % {Feb. 2021 - PRESENT} % Date(s)
  % {
  %   \begin{cvitems} % Description(s) of what you did
  %     \item {Built a social network for EWAAB members, allowing 100+ users to create public posts, react to comments, and subscribe to email notifications.}
  %     % \item {Uses markdown to format text content, and sharp to resize media. Designed using REST and GraphQL, implemented in Node.js and Typescript.}
  %   \end{cvitems}
  % }

  %---------------------------------------------------------
\end{cventries}
